Constructing a universe for the setoid model

### 2020-07-07 paper.tex
orcid

\author{Thorsten Altenkirch}{School of Computer Science, University of Nottingham, UK}{psztxa@nottingham.ac.uk}{orcid}{Supported by USAF grant FA9550-16-1-0029.}
\author{Simon Boulier}{Inria, Nantes, France}{simon.boulier@inria.fr}{}{}
\author{Ambrus Kaposi}{E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary}{akaposi@inf.elte.hu}{orcid}{Supported by the National Research, Development and Innovation Fund of Hungary, financed under the Thematic Excellence Programme funding scheme, Project no. ED\_18-1-2019-0030 and the Bolyai Fellowship of the Hungarian Academy of Sciences, Project no.\ BO/00659/19/3.}
\author{Christian Sattler}{Chalmers University of Technology, Gothenburg, Sweden}{sattler@chalmers.se}{}{Supported by USAF grant FA9550-16-1-0029 and Swedish Research Council grant 2019-03765.}
\author{Filippo Sestini}{School of Computer Science, University of Nottingham, UK}{Filippo.Sestini@nottingham.ac.uk}{}{}

>>>>

\author{Thorsten Altenkirch}{School of Computer Science, University of Nottingham, UK}{psztxa@nottingham.ac.uk}{https://orcid.org/0000-0002-6582-5025}{Supported by USAF grant FA9550-16-1-0029.}
\author{Simon Boulier}{Inria, Nantes, France}{simon.boulier@inria.fr}{}{}
\author{Ambrus Kaposi}{E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary}{akaposi@inf.elte.hu}{https://orcid.org/0000-0001-9897-8936}{Supported by the National Research, Development and Innovation Fund of Hungary, financed under the Thematic Excellence Programme funding scheme, Project no. ED\_18-1-2019-0030 and the Bolyai Fellowship of the Hungarian Academy of Sciences, Project no.\ BO/00659/19/3.}
\author{Christian Sattler}{Chalmers University of Technology, Gothenburg, Sweden}{sattler@chalmers.se}{}{Supported by USAF grant FA9550-16-1-0029 and Swedish Research Council grant 2019-03765.}
\author{Filippo Sestini}{School of Computer Science, University of Nottingham, UK}{Filippo.Sestini@nottingham.ac.uk}{}{}
